% vitae.tex (Curriculum Vitae)

\addcontentsline{toc}{chapter}{Vita}
\chapter*{Vita}

George Ekow Quaye was born on May 16, 1991. He graduated from Adidome Senior High School, Ghana in 2011. George was a beneficiary, Government Scholarship for Best Science Student, and also earn an award for the best graduating science student in Adidome Senior High School. George, having taken an equal number of classes in Statistics, Economics, and Mathematics as an Actuarial Science student and excelled in them, successfully graduated in 2016 with a Bachelor of Science (BS) degree in Actuarial Science at the University of Cape Coast. This feat, coupled with his dutiful nature and research interests, earned him a one-year position as a Research Assistant in one of the school’s prestigious departments, The Department of Clinical Nutrition and Dietetics. With his background, he tutored in courses related to statistics, he collected, analyzed, and interpreted statistical data for four different projects, two of which are: \textit{The Prevalence of Anaemia in Adolescent Girls and Women in Ghana} with Michigan State University in collaboration with Ghana’s flagship the University of Ghana as well as, \textit{Iron Status and Psychosocial Well-being of Pregnant Women in Ghana} with Pennsylvania State University in collaboration with the University of Cape Coast. These projects helped him to practically acquire the systematic procedure, knowledge, and technical skills in collecting both qualitative and quantitative data, organizing, analyzing using the appropriate statistical tool, and giving interpretation based on the output, and making necessary inferences. Also, as a supervisor on one of these taught him how to lead, plan, schedule, and interviewed a participant in data collection. He is currently a graduate student majoring in Statistics at the University of Texas at El Paso (UTEP) and working at the Department of Mathematical Sciences of UTEP as a graduate teaching assistant, where he tutor at the Mathematics Resource Center for Students (MARCS) and grade scripts for assigned Professors and classes and expected to graduate in May 2021. As required by a graduate study,  he started working on a research topic, \textit{Making valid inference with decision trees} as his thesis with one of the elite professors in the department in person of Professor Xiaogang Su in his second year of Master's Studies. George will pursue his doctoral degree in Data Science at the  University of Texas at El Paso (UTEP) in El Paso where he is currently obtaining his Master's degree in Statistics.\newline
Email: gequaye@miners.utep.edu



%After obtaining his Master’s degree,





